```{r results='asis', echo=FALSE}

github.organization <- "geohazards-tep"
source('../R/global.R')

# load packages
suppressMessages(library("rjson"))
suppressMessages(library("RCurl"))  

# global chunk options
 opts_chunk$set(cache=FALSE, autodep=TRUE)

repo.frame <- GetRepos(github.organization)
```

# Geohazards TEP GitHub Guide

#### Updated: `r format(Sys.Date(), format="%d %B %Y")`

This guide provides a quick reference to the geohazards-tep GitHub organization repositories.

The guide is structured in chapters:

* The first chapter provides an overview of the ESA's Geohazards Exploitation Platform.
* The second explains you how you can pickup on one of the existing repositories and build your own application to process Earth Observation data on the Geohazards Exploitation Platform
* The third joins all repositories hosting conventional InSAR techniques such as interferogram generation with ROI_PAC, GMTSAR and DORIS (via Adore)
* The fourth includes the advanced InSAR techniques such as PS processing with StaMPS
* The fifth describes the auxiliary services of the Geohazards Exploitation Platform e.g. DEM generation for ROI_PAC, GMTSAR and Gamma
* The sixth chapters includes the application built using Toolboxes such as NEST or Sentinel-1 Toolbox
* The seventh and final chapter provides application templates that can be cloned and then linked to another remote repository in the GitHub organization to build new applications

## Repository description

Each repository entry is structured with several sections:

* A short table including some facts about the repository e.g. last update, how many forks, how many stars
* An introduction about the repository content and goal
* A Getting Started section
* The application installation steps including pre-requisites of the development version and releases
* The instructions on how to submit the processing workflow or how to use the template
* Links to the community and documentation for the given repository
* The list of project members having participated in the repository content
* How to submit questions, suggestions or issues
* The software licence associated to the repository

## Some useful links about the ESA Geohazards Exploitation Platform

The platform URL is https://geohazards-tep.eo.esa.int/

The Twitter account is @ESA_tep

The Tumblr blog to follow is http://geohazards-tep.tumblr.com/

## Want to become part of the Geohazards Exploitation Platform community?

Send an expression of interest to <a href="mailto:geohazards-tep@esa.int">geohazards-tep@esa.int</a>

##### `r format(Sys.Date(), format="%d %B %Y")`

### Meet the team

```{r results='asis', echo=FALSE}

members <- GetPublicMembers(github.organization)

members$Members <- paste0("<a href='", members$url, "'><img style='float: left' src='", members$avatar,"' width='35' height='35'>", members$login, "</a>")

kable(members[ , which(names(members) %in% c("Members"))], row.names = FALSE, format = "html", escape = FALSE)

```

### A few facts about the geohazards-tep GitHub organization

#### Top Starred repositories

```{r results='asis', echo=FALSE}

stars <- unique(repo.frame[ , which(names(repo.frame) %in% c("Project", "Stars"))])

stars <- stars[stars$Stars>0.0, ]

kable(head(stars[order(-stars$Stars), ], 5), row.names = FALSE, format = "html")
```

#### Top Forked repositories

```{r results='asis', echo=FALSE}

forks <- unique(repo.frame[ , which(names(repo.frame) %in% c("Project", "Forks"))])

forks <- forks[forks$Forks>0.0, ]

kable(head(forks[order(-forks$Forks), ], 5), row.names = FALSE, format = "html")
```

#### Programming Languages

```{r results='asis', echo=FALSE}
pie(table(as.factor(repo.frame[ ,"Language"])))
```
